---
title: "Hypothesis Testing on ToothGrowth Data"
author: "Ann Crawford"
date: "September 7, 2017"
output: pdf_document
subtitle: Statistical Inference Project Part II, Class 6 in data science series
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Dependencies
```r
##install.packages("dplyr")

```
## Tooth Growth Data
The standard R data set, ToothGrowth,  measures the effect of Vitamin C on tooth growth in guinea pigs
The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one 
of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery 
methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC).

```{r ToothGrowth}
summary(ToothGrowth)
```
## Hypotesis Testing
The sample data graph (see Appednix) implies two Hypothesis: 
1. Supply using orange juice as the delivery method induces longer tooth growth. 
2. Increase of vitamin C does induces longer tooth growth.
---
## Testing the affect of supp, delivery method
**HO = mean OJ = mean VC**
Divide the data into two groups, OJ and VC. And run an unpaired t test on the groups.  T
```{r}
library(dplyr)
library(magrittr) # for %$% extraction

OJ <- ToothGrowth %>% filter(supp=="OJ")
VC <- ToothGrowth %>% filter(supp=="VC")

t.test(OJ$len, VC$len)

```
----
## There are 3 groups of doses, 0.5, 1, 2
  Divide the data into 3 groups, OJ and VC and run t test. 
```{r}

low     <- ToothGrowth %>% filter(dose == 0.5)
medium  <- ToothGrowth %>% filter(dose == 1)
high    <- ToothGrowth %>% filter(dose == 2)

t.test(low$len, high$len)

t.test(medium$len, high$len)
```
#Appendix

```{r pressure, echo=FALSE}
require(graphics)
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
       xlab = "ToothGrowth data: length vs dose, given type of supplement")
```
