---
title: "Central Limit Theorem"
author: "Ann Crawford"
highlighter: highlight.js
output:
  html_document: default
  pdf_document: default
mode: selfcontained
hitheme: tomorrow
subtitle: Statistical Inference Project Part I, Class 6 in data science series
framework: io2012
url:
  assets: ../../assets
  lib: ../../librariesNew
widgets: mathjax
---
## Central Limit Theorem 

- The Central Limit Theorem (CLT) states that the distribution of averages of independent and identically distributed (iid) variables becomes that of a **standard normal** as the sample size increases even if the original variables are not normally distrubted. 

---
##http://t-redactyl.io/blog/2016/02/creating-plots-in-r-using-ggplot2-part-7-histograms.html
## Example plotting means
### CTL demonstartion using 
```{r ,fig.height=3.5,fig.width=8, fig.align='center', echo = FALSE}
library(ggplot2)
lambda <- 0.2
m <- 40
n <- 10000 # sample size
mean1 <- 1/lambda
stddv <- 1/ lambda
mm <-data.frame((apply(matrix(rexp(m*n,lambda),nrow = n/m, ncol= n),1,mean)))
colnames(mm)= c("x")
    g <- ggplot(mm, aes(x = x))
    g <- g + geom_histogram(bins = 25) 
    g <- g + geom_vline(xintercept = 1/lambda, size = 2)
    g <- g + labs(title = paste('mu = 1/lambda =', 1/lambda ,' sample size = ', n))
    g
```
## Example plotting sd
### CTL demonstartion using 
```{r ,fig.height=3.5,fig.width=8, fig.align='center', echo = FALSE}
library(ggplot2)
lambda <- 0.2
m <- 40
n <- 10000 # sample size
mean1 <- 1/lambda
stddv <- 1/ lambda
mm <-data.frame((apply(matrix(rexp(m*n,lambda),nrow = n/m, ncol= n),1,sd)))
colnames(mm)= c("x")
    g <- ggplot(mm, aes(x = x))
    g <- g + geom_histogram(bins = 25) 
    g <- g + geom_vline(xintercept = 1/lambda, size = 2)
    g <- g + labs(title = paste('sd = 1/lambda =', 1/lambda ,' sample size = ', n))
    g
```
---
## Using manipulate
```
library(manipulate)
myHist <- function(mu){
  hist(galton$child,col="blue",breaks=100)
  lines(c(mu, mu), c(0, 150),col="red",lwd=5)
  mse <- mean((galton$child - mu)^2)
  text(63, 150, paste("mu = ", mu))
  text(63, 140, paste("Imbalance = ", round(mse, 2)))
}
manipulate(myHist(mu), mu = slider(62, 74, step = 0.5))
```

---
