---
title: "Hypothesis Testing on ToothGrowth Data"
author: "Ann Crawford"
date: "September 7, 2017"
output: pdf_document
subtitle: Statistical Inference Project Part II, Class 6 in data science series
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r }

# Clear our workspace
rm(list=ls())
#Dependencies
##install.packages("dplyr")
##install.packages("ggplot")
##install.packages("gridExtra")

library(magrittr) # for %$% extraction
library(ggplot2)
library(grid)
library(gridExtra)
library(dplyr)
```
```{r setup}
# Clear our workspace
rm(list=ls())
```
## Tooth Growth Data
The standard R data set, ToothGrowth,  measures the effect of Vitamin C on tooth growth in guinea pigs
The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one 
of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery 
methods, (orange juice or ascorbic acid (a form of vitamin C and coded as VC).

```{r ToothGrowth}
summary(ToothGrowth)
```
## Hypotesis Testing using T Test.
Visually examine the sample data graphs (see Appednix). The graphs lend evidence to the t test assumptions.
Based on the graphs the following Null hypothesi will be tested: 
1. Supply using orange juice as the delivery method induces longer tooth growth. 
2. Increase of vitamin C does induces longer tooth growth.
* Assumptions for t tests:
+ Data includes trials from 60 independent guinea pigs. 
+ Data are iid normal.
+ The distribution of the data is roughly symmetric and mound shaped

### Testing the affect of supp, delivery method
Assume Null hypothesis the tooth growth is greater for OJ., 
Divide the data into two groups, OJ and VC. 

P value is the probablity of observing a test statistic as large as the one calculated assuming H is true.

```{r, warning=FALSE}

OJ <- ToothGrowth %>% filter(supp=="OJ") 
VC <- ToothGrowth %>% filter(supp=="VC")

t.test(OJ$len, VC$len, alternative = "greater", paired = FALSE, conf.level = 0.95)
```
### Testing the affect of dose
There are 3 groups of doses, 0.5, 1, 2.  Divide the data into 3 groups, OJ and VC and run two t tests.
Test that more dosage leads to longer tooth growth.
  
```{r}
low     <- ToothGrowth %>% filter(dose == 0.5)
medium  <- ToothGrowth %>% filter(dose == 1)
high    <- ToothGrowth %>% filter(dose == 2)

t.test( high$len, low$len,alternative = "greater", paired = FALSE, conf.level = 0.95,Var.equal=FALSE)
t.test(high$len, medium$len,alternative = "greater", paired = FALSE, conf.level = 0.95,Var.equal=FALSE)
```
##Conclusion
The p values and confidence intervals returned from the above tests return low p-values conclude:
Accept Null hypothises that mean tooth length of OJ is statisically significant greater than VC.
Accept Null hypothises that mean tooth lenght of higher doses is statistically significant greater than lower doeses.  

#Appendix

```{r append1, echo=FALSE}
require(graphics)
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
       xlab = "ToothGrowth data: length vs dose, given type of supplement")
```

```{r append2, echo=FALSE}
# plot densities 
library(ggplot2)
library(gridExtra)
totalS <- rbind(OJ,VC)
ggplot(totalS, aes(len, fill = supp)) + geom_density(alpha = 0.2)

ToothGrowth2 <- ToothGrowth
ToothGrowth2$supp <- as.factor(ToothGrowth2$supp)
p <- ggplot(ToothGrowth2, aes(x=supp, y=len, fill=supp))+
  geom_violin() + labs(fill = "Supplier") 

#plot distributions of doses
ToothGrowth2$dose <- as.factor(ToothGrowth2$dose)
p1 <- ggplot(ToothGrowth2, aes(x=dose, y=len, fill=dose))+
  geom_violin()  + labs(fill = "Dose (mg)") 

 grid.arrange(p1, p, ncol=2)
```
